%-----------WORK EXPERIENCE & PROJECTS-----------%
\section{Work Experience}
\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{Summer Internship: Aon Reinsurance Actuary}}{Jun 2025 — Aug 2025}
    \resumeItemListStart
        \resumeItem{Developed and presented statistical models for data analysis and forecasting retrocession contract pricing.}
        \resumeItem{Learnt and applied VBA to quickly develop an Excel Macro which improved data mining efficiency by 300\%.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{HSBC Personal Banking \& Accuracy Transactions Insight Weeks}}{Apr 2025}
    \resumeItemListStart
        \resumeItem{Networked and collaborated at HSBC's Personal Banking written \& verbal communication workshops.}
        \resumeItem{Collaborated on a case study with Accuracy to develop  discounted cash flow and enterprise value models.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{School Uniform Website}}{Jan 2021 — Feb 2022}
    \resumeItemListStart
        \resumeItem{Implemented and maintained a website with technology to query stock from a real-time database.}
        \resumeItem{Presented and clearly communicated the product for use with a free school uniform charity.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{Black-Scholes-Vasicek Research Project}}{Apr 2025}
    \resumeItemListStart
        \resumeItem{Independently researched and analysed risk measures on options with stochastic interest volatility in Python.}
        \resumeItem{Communicated and presented findings with a researcher at Imperial College London.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{JavaScript Standard Library Contributor}}{Apr 2025}
    \resumeItemListStart
        \resumeItem{Implemented, backtested, and validated a moving average trading strategy showcase of the library.}
        \resumeItem{Programmed a package that computes sliding window statistics from an input data stream.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{AI Agents Hackathon}}{Mar 2025 — Apr 2025}
    \resumeItemListStart
        \resumeItem{Collaborated on the research and development of a machine learning algorithm that reads important documents.}
        \resumeItem{Engineered and optimised translations, summaries, and the signposting of relevant resources.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Implied Volatility Research Project}}{Oct 2024}
    \resumeItemListStart
        \resumeItem{Reviewed cutting-edge research on the market's response to Brexit and applied it to analyse the US Election.}
        \resumeItem{Built a predictive model in Python using stochastic differential equations and jump processes to quantify volatility.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Wiki Administrator}}{2021-2025}
    \resumeItemListStart
        \resumeItem{Contributed 7773 edits to an open-source \href{https://corepunk.wiki/w/index.php?target=Stratonian&title=Special\%3AContributions}{Wiki} as an administrator, communicating regularly with readers.}
        \resumeItem{Wrote and researched for hundreds of articles—developing templates, data structures, and user interface.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Chatbot \& Finance Simulation}}{Jul 2020 — Sep 2022}
    \resumeItemListStart
        \resumeItem{Designed and implemented a chatbot which used the Wikipedia API to quiz users and measure their typing speed.}
        \resumeItem{Developed a stock market simulator which increased user engagement. Users could buy and sell virtual stocks.}
    \resumeItemListEnd
\resumeSubHeadingListEnd