%-----------Work Experience-----------%
\section{Work Experience \& Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{AI Agents Hackathon}}{2025}
    \resumeItemListStart
        \resumeItem{Led the research and development of a Natural Language Processor that reads important documents.}
        \resumeItem{Engineered and optimised translations, summaries, and the signposting of relevant resources.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Black-Scholes Research}}{2025}
    \resumeItemListStart
        \resumeItem{Simulated and quantified the performance of different risk measures for options pricing.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{JavaScript Standard Library Contributor}}{2025}
    \resumeItemListStart
        \resumeItem{Developed a moving average trading strategy implementation of the library.}
        \resumeItem{Programmed a package that computes sliding window statistics from an input data stream.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Hackathon Organiser}}{2024-2025}
    \resumeItemListStart
        \resumeItem{Organised and coordinated IC Hack—Europe's largest student-run hackathon.}
        \resumeItem{Negotiated optimal prices with various caterers.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Wiki Administrator}}{2021-2025}
    \resumeItemListStart
        \resumeItem{Contributed 7773 edits to a \href{https://corepunk.wiki/w/index.php?target=Stratonian&title=Special\%3AContributions}{Wiki} as an administrator.}
        \resumeItem{Wrote and researched for hundreds of articles—developing templates, data structures, and user interface.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Private Tutor}}{2022-2024}
    \resumeItemListStart
        \resumeItem{Planned and delivered engaging free lessons to GCSE students in need.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Blog Website}}{2022-2023}
    \resumeItemListStart
        \resumeItem{Programmed, hosted, and maintained a blog website with search, tagging, and comment functionality.}
        \resumeItem{Examined and solved interesting problems in finance and the sciences.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{School Uniform Website}}{2021-2022}
    \resumeItemListStart
        \resumeItem{Implemented a website allowing users to search, sort, and order stock from a database that updated in real-time.}
        \resumeItem{Presented and released the product for use with a free school uniform charity.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Chatbot \& Finance Simulation}}{2020-2022}
    \resumeItemListStart
        \resumeItem{Designed and implemented a chatbot which used the Wikipedia API to quiz users and measure their typing speed.}
        \resumeItem{Developed a stock market simulator which increased user engagement. Users could buy and sell virtual stocks.}
    \resumeItemListEnd

\resumeSubHeadingListEnd